---
title:compwrap (Comparison Wrapper functions)
author: Toshiaki Ara
date: "`r Sys.Date()`"
---

# Introduction

This package contains two wrapper functions.

1. brunner.munzel.test in lawstat package
2. posthocTGH in userfriendlyscience package

These functions in compwrap package accept formula.

Also, this package provide a function for
 permuted Brunner-Munzel test
 in the case of small sample size.

# Installation

```{r, eval=FALSE}
library(devtools)
install_github("toshi-ara/compwrap")
```

# Example
## Brunner-Munzel test
```{r, message=FALSE}
Y <- c(1, 2, 1, 1, 1, 1, 1, 1, 1, 1, 2, 4, 1, 1)
N <- c(3, 3, 4, 3, 1, 2, 3, 1, 1, 5, 4)

dat <- data.frame(
    value = c(Y, N),
    group = factor(rep(c("Y", "N"), c(length(Y), length(N))),
                   levels = c("Y", "N"))
)

library(compwrap)

## Default
brunner.munzel.test(Y, N)

## Formula interface
brunner.munzel.test(value ~ group, data = dat)
```

## permuted Brunner-Munzel test

`brunner.munzel.permutation.test` takes time to obtain results.

```{r, message=FALSE}
library(compwrap)

Y <-  c(1,2,1,3,1,2,2,4,1,1)
N <-  c(3,4,5,2,3,2,1,5,4,3)

dat <- data.frame(
    value = c(Y, N),
    group = factor(rep(c("Y", "N"), c(length(Y), length(N))),
                   levels = c("Y", "N"))
)

## Default
brunner.munzel.permutation.test(Y, N)

## Formula interface
brunner.munzel.permutation.test(value ~ group, data = dat)
```

### Comparison with other methods

```{r, message=FALSE}
# Wilcoxson sum-rank test
wilcox.test(value ~ group, data = dat)

# exact Wilcoxson sum-rank test
library(coin)
wilcox_test(value ~ group, data = dat, distribution = "exact")
```

## Tukey test and Games-Howell test

```{r, include=FALSE}
library(compwrap)
```

### Tukey method

```{r, message=FALSE}
## Default
posthocTGH(y=ChickWeight$weight, x=ChickWeight$Diet, method="tukey")

## Formula interface
posthocTGH(weight ~ Diet, data = ChickWeight, method="tukey")
```

### Games-Howell method (default)

```{r, message=FALSE}
## Default
posthocTGH(y=ChickWeight$weight, x=ChickWeight$Diet)

## Formula interface
posthocTGH(weight ~ Diet, data = ChickWeight)
```

